Dragonfly Territory Ananlysis

### 2020-11-24 analysis/analysisSS.Rmd
data manip work

iEleganSAY <- dplyr::rename(iElegansAY, iElegans_abundance = ABUNDANCE)
cPuellaSAY <- 
lSponsaSAY <- 
lQuadrimaculataSAY <- 
sStriolatumSAY <-

@@

dragonflyYears <- c(1959:1988)

@@

bPratenseCompAY <- data.frame(bPratenseAbundance, dragonflyYears)
pNymphulaCompAY <- data.frame(pNymphulaAbundance, dragonflyYears)
aCyaneaCompAY <- data.frame(aCyaneaAbundance, dragonflyYears)
sSanguineumCompAY <- data.frame(sSanguineumAbundance, dragonflyYears)
aGrandisCompAY <- data.frame(aGrandisAbundance, dragonflyYears)

# Damselfly Larval Data

larval_data <- read.csv("~/GitHub/rrirfinalproject/larval_data.csv")

>>>>

iElegansSAY <- dplyr::rename(iElegansAY, iElegans_abundance = ABUNDANCE)
cPuellaSAY <- dplyr::rename(cPuellaAY, cPuella_abundance = ABUNDANCE)
lSponsaSAY <- dplyr::rename(lSponsaAY, lSponsa_abundance = ABUNDANCE)
lQuadrimaculataSAY <- dplyr::rename(lQuadrimaculataAY, lQuadrimaculata_abundance = ABUNDANCE)
sStriolatumSAY <- dplyr::rename(sStriolatumAY, sStriolatum_abundance = ABUNDANCE)

@@

YEAR <- c(1959:1988)

@@

bPratenseCompAY <- data.frame(bPratenseAbundance, YEAR)
pNymphulaCompAY <- data.frame(pNymphulaAbundance, YEAR)
aCyaneaCompAY <- data.frame(aCyaneaAbundance, YEAR)
sSanguineumCompAY <- data.frame(sSanguineumAbundance, YEAR)
aGrandisCompAY <- data.frame(aGrandisAbundance, YEAR)

# I am going to join these 10 dataframes by the common column year
# I want year on the far left so I am going to reorder the first dataframe that will determine the order of my join function

bPratenseCompAY2 <- subset(bPratenseCompAY, select = c(2,1))

join1 <- dplyr::left_join(bPratenseCompAY2, pNymphulaCompAY, by= NULL)
join2 <- dplyr::left_join(join1, aCyaneaCompAY, by = NULL)
join3 <- dplyr::left_join(join2, sSanguineumCompAY, by = NULL)
join4 <- dplyr::left_join(join3, aGrandisCompAY, by = NULL)
join5 <- dplyr::left_join(join4, cPuellaCompAY, by = NULL)
join6 <- dplyr::left_join(join5, iElegansCompAY, by = NULL)
join7 <- dplyr::left_join(join6, lSponsaCompAY, by = NULL)
join8 <- dplyr::left_join(join7, lQuadrimaculataCompAY, by = NULL)
fullAbundanceDF <- dplyr::left_join(join8, sStriolatumCompAY, by = NULL)

# I want a total for each year

abundanceSums <- data.frame(rowSums(fullAbundanceDF[,c(2,3,4,5,6,7,8,9,10,11)]))
